
\begin{thebibliography}{1}


\bibitem{adl} Michael Gelfond, Vladimir Lifschitz, \emph{Action Languages} Linköping Electronic Articles in
Computer and Information Science
Vol. 3(1998): nr 16. Dostępne w http://citeseerx.ist.psu.edu/viewdoc/download?doi= 10.1.1.146.4665\&{}rep=rep1\&{}type=pdf [Dostęp 15.01.2014]
\bibitem{eclipsearticle}Kim Moir, \emph{The Architecture of Open Source Application}, Dostępne w http://www.aosabook.org/en/eclipse.html [Dostęp: 19.01.2014]
\bibitem{ai} Stuart Russell, Peter Norvig, \emph{Artificial Intelligence: A
Modern Approach (2nd ed.)}, Upper Saddle River, New Jersey: Prentice Hall, 2003.
ISBN 0-13-790395-2
\bibitem{compilersEN}A. Aho et al., \emph{Compilers: principles,
techniques, and tools} Pearson Education, 2007.
\bibitem{pddl3.1}Daniel L. Kovacs, \emph{Complete BNF description of PDDL 3.1 (completely corrected).} 2011. Dostępny w: http://www.plg.inf.uc3m.es/ipc2011-deterministic/attachments/OtherContributions/kovacs-pddl-3.1-2011.pdf [Dostęp: 18.01.2014]
\bibitem{npdl} Jeremy Frank, Ari Jonsson, \emph{Constraint-based Attribute and Interval Planning.} 2002. Dostępne w:
http://ti.arc.nasa.gov/m/pub-archive/313h/0313\%20\%28Frank\%29.pdf [Dostęp: 18.01.2014] 
\bibitem{antlr}T.~Parr, \emph{The Definitive ANTLR Reference. Building Domain-Specific Languages}. 
The Pragmatic Bookshelf, 2007.
\bibitem{eclipseinaction} David Gallardo et al., \emph{Eclipse in Action: A Guide for the Java Developer}, Chapter 8,9, Manning, 2003.
\bibitem{eclipseplugins}E.~Clayberg, D.~Rubel, \emph{Eclipse Plug-Ins (3 ed.)}. Addison-Wesley Professional, 2008. 
\bibitem{fdalgorytm} Malte Helmert, \emph{The Fast Downward Planning System}. Journal of Artifcial Intelligence Research 26 (2006), str. 191-246. Dostępne w: https://www.jair.org/media/1705/live-1705-2731-jair.pdf [Dostęp: 18.01.2014]
\bibitem{webpddl} Dejing Dou, \emph{The Formal Syntax and Semantics of Web-PDDL} Dostępne w: http://aimlab.uoregon.edu/web-pddl.pdf [Dostęp: 18.01.2014]
\bibitem{compilers}A. Aho i inni, \emph{Kompilatory. Reguły, metody i narzędzia}.
WNT, 2001.
\bibitem{opt} Drew McDermott, \emph{OPT Manual.} 2005. Dostępny w: http://www.cs.yale.edu/homes/dvm/papers/opt-manual.pdf [Dostęp: 18.01.2014]
\bibitem{planning} I.Vlahavas, I.Refanidis, \emph{Planning and Scheduling.} Dostępny w: http://www.eetn.gr/index.php/eetn-publications/ai-research-in-greece/planning-and-scheduling [Dostęp: 18.01.2014]
\bibitem{pddl}M. Ghallab et al., \emph{PDDL -- The Planning Domain Definition Language. Version 1.2}.
AIPS Conference, 1998.
\bibitem{pddlplus} Maria Fox, Derek Long, \emph{PDDL+ : Modelling Continuous Time-dependent Effects}. Dostępne w: http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.15.5965 \&{}rep=rep1\&{}type=pdf [Dostęp: 18.01.2014]
\bibitem{ppddl} Hakan L. S. Younes, Michael L. Littman, \emph{PPDDL1.0: An Extension to PDDL for Expressing
Planning Domains with Probabilistic Effects.} 2004. Dostęp w: http://reports-archive.adm.cs.cmu.edu/anon/2004/CMU-CS-04-167.pdf [Dostęp: 18.01.2014]
\bibitem{satplan} Henry Kautz, \emph{SATPLAN04: Planning as Satisfiability.} 1992. Dostępne w:
http://www.tzi.de/~edelkamp/ipc-4/Proc/satplan04.pdf [Dostęp: 18.01.2014]
\bibitem{strips} Richard E. Fikes, Nils J. Nilsson, \emph{Strips: A new approach to the application of theorem proving to problem solving.} International Joint Conferences on Artificial Intelligence, 1971.







\end{thebibliography}
